Presentasjon OPX Fiffig tittel

### 2022-08-01 Presentasjon/presentasjon.Rmd
Flere enkel navn på bildefiler
Flere bildefiler

## <br> OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients

## <br> How to assess financial performance?
- Data collection 
- Key Performance Indicators

```{r, fig.align='center'}
knitr::include_graphics("Images/kpi.png")

@@

## {data-background="Images/9-Brainstorming-techniques-to-come-up-with-great-ideas.png" data-background-size=cover}

>>>>

## <br> OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients <br>

```{r, out.height="128px", out.width="568px", fig.align='center'}
knitr::include_graphics("Images/logo_opx.png")
```

## <br> How to assess financial performance?
- Data collection 
- Key Performance Indicators <br>

```{r, out.height="268px", out.width="350px", fig.align='center'}
knitr::include_graphics("Images/kpi.png")

@@

## {data-background="Images/brainstorming2.png" data-background-size=cover}
